\section{Test Results}
We test proposed techinque using the use cased explained in the previouse section.

\subsection{Verification of Results}
%TODO: when we have something to compare with

\subsection{Fuel Consumption}
The purpose of \tech is to reduce fuel consumption. 
We use SUMO's build-in function to calculate the vehicles fuel consumption, which is explained in \cite{SUMOFuel}.

%Figure~\ref{tik:fuel:0:51} shows this fuel consumption as a function of time for vehicles driving on route 51 controlled by SUMO only. 
%Figure~\ref{tik:fuel:100:51} shows the same setup, but with all vehicles controlled by \tech.
Figure~\ref{tik:fuel:avg} plots the average fuel consumption for vehicles driving on all routes. 
The results clearly show that using \tech in this setup will reduce the fuel consumption significantly.
Acrose all routes, we see a reduction from an average of 130 $mL$ to an average of 96 $mL$, which is a reduction of 29 \%.
If we only look at route 51, we observe an average fuel consumption without \tech at 175 $mL$, and 117 $mL$ with \tech.
This is again a significant reduction in fuel consumption in 33 \%.

%\input{TestResults/100/fuel_51.tex}
%\input{TestResults/0/fuel_51.tex}

\begin{figure}
\begin{tikzpicture}
\begin{axis}[xlabel=Route identifiers,ylabel=Fuel consumption,bar width=1pt]
\addplot[ybar, blue] table[x=Route,y=Fuel] {TestResults/0/avg.dat};
\addplot[ybar, red] table[x=Route,y=Fuel] {TestResults/100/avg.dat};
\draw[thick, red] (axis cs:0,94) -- (axis cs:109,94);
\draw[thick, blue] (axis cs:0,131) -- (axis cs:109,131);
\end{axis}
\end{tikzpicture}
\caption{Average fuel consumption with (red) and without \tech (blue)}\label{tik:fuel:avg}
\end{figure}


\subsection{Distance}
Figure~\ref{tik:distance:0:51} shows the distance ?? vehicles drive on route ?? as a function of time when their driving behaviour is solely controled by SUMO. 
The vehicle is stationary whenever the curve flatens.
From the figure we clearly see that the vehicles on this route has to stop four times, at 250 meter, at 550 meters, at 800 meters and again at 1100 metets.

When we control the speed of the vehicles using \tech, we see a different result showed in Figure~\ref{tik:distance:100:51}.
The curves in this figure are much more smooth, and fewer vehicles has to stop completely at a cross section.
Some vehicles have to stop due to blocking vehicles or cross traffic, which we do not take into account.

We can therefore see that using \tech results in less full stops.
%\input{TestResults/0/distance_51.tex}
%\input{TestResults/100/distance_51.tex}

\subsection{Speed}
Figure~\ref{tik:speed:0:51} shows the speed at which SUMO controlled vehicles on route 51 drive as a function over time.
The graph clearly shows that the vehicles quicly accelerates up to the maximal speed, then quickly decelerates to a full stop and then quickly accelerates again.
By using \tech we see a very different outline (See Figure~\ref{tik:speed:100:51}).
Few vehicles decelerates to $0 m/s$, and many stay above $5 m/s$ ($18 km/h$ or $11$ miles per hour ($mph$)).
We do, however, still see a large fluctuation.
%\input{TestResults/100/speed_51.tex}
%\input{TestResults/0/speed_51.tex}

\subsection{Time}
It is interesting to investigate wether driving after \tech results in longer travel time than without.
It takes on average 114 seconds to drive a route in our test without \tech, and when all vehicles drive with \tech it takes 111 seconds. 
We therefore do not see any significant differens in thees results.


